---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

`"binomial"` is a minimal [R](http://www.r-project.org/) package that implement functions for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.

* `bin_choose()` calculates the number of combinations of successes in multiple trials.
* `bin_probability()` calculates the probability of successes in multiple trials.
* `bin_distribution()` shows a data frame (with two classes: `"bindis"` and `"data.frame"`) with the probability distribution.
* `bin_cumulative()` shows a data frame (with two classes: `"bincum"` and `"data.frame"`) with the binomial cumulative distribution.
* `bin_variable()` shows a list of class `"binvar"` with named elements `trials` and `prob`.
* `bin_mean()` calculates the mean of a binomial distribution.
* `bin_variance()` calculates the variance of a binomial distribution.
* `bin_mode()` calculates the mode of a binomial distribution.
* `bin_skewness()` calculates the skewness of a binomial distribution.
* `bin_kurtosis()` calculates the kurtosis of a binomial distribution.
* `plot()` method for a `"bindis"` object to display the probability histogram of a binomial distribution.
* `plot()` method for a `"bincum"` object to graph the binomial cumulative distribution.
* `summary()` method for a `"binvar"` object.


## Motivation

This package has been developed to illustrate some of the concepts
behind the creation of an R package.


## Installation

Install the development version from GitHub via the package `"devtools"`:

```r
# development version from GitHub:
#install.packages("devtools") 
# install "binomial" (without vignettes)
devtools::install_github("stat133-sp19/hw-stat133-feng1128/binomial")
# install "binomial" (with vignettes)
devtools::install_github("stat133-sp19/hw-stat133-feng1128/binomial", build_vignettes = TRUE)
```


## Usage

```{r}
library(binomial)

# the number of combinations in which 2 successes can occur in 5 trials
choose_successes <- bin_choose(n = 5,k = 2)
choose_successes

# the probability of getting 2 successes in 5 trials
# assume the probability of success in each trial is 0.5
p <- bin_probability(success = 2, trials = 5, prob = 0.5)
p

# the probability distribution of 5 trials
# assume the probability of success in each trial is 0.5
dis1 <- bin_distribution(trials =5, prob = 0.5)
dis1
# plot the histogram of the distribution
plot(dis1)

# the binomial cumulative distribution of 5 trials
# assume the probability of success in each trial is 0.5
dis2 <- bin_cumulative(trials =5, prob = 0.5)
dis2
# plot the cumulative distribution
plot(dis2)

# the list of the binomial probability of 5 trials
# assume the probability of success in each trial is 0.5
bin1 <- bin_variable(trials =5, prob = 0.5)
bin1
# summary
summary(bin1)

# the mean of 5 trials with the probability of success = 0.5 in each trial
me <- bin_mean(5, 0.5)
me

# the variance of 5 trials with the probability of success = 0.5 in each trial
v <- bin_variance(5, 0.5)
v

# the mode of 5 trials with the probability of success = 0.5 in each trial
mo <- bin_mode(5, 0.5)
mo

# the skewness of 5 trials with the probability of success = 0.5 in each trial
s <- bin_skewness(5, 0.5)
s

# the kurtosis of 5 trials with the probability of success = 0.5 in each trial
k <- bin_kurtosis(5, 0.5)
k
```
