---
title: "Binomial Distribution"
author: "Chengcheng Feng"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial distribution}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial Distribution

The package `"binomial"` is created to implement functions for calculating probabilities of a Binomial random variable, and related calculations such as the
probability distribution, the expected value, variance, etc.


## Calculate the combinations of successes in trials

The function `bin_choose()` is used to calculate the number of combinations in which k successes can occur in n trials.

```{r}
choose_successes <- bin_choose(n = 5,k = 2)
choose_successes
```

There are two arguments: `n` and `k`. `n` means the number of trials and `k` represents the number of successes. Here `n` should be not less than `k`.


## Calculate the probability of successes in trials

The function `bin_probability()` is used to calculate the probability of successes in multiple trials.

```{r}
probability_successes <- bin_probability(success = 2, trials = 5, prob = 0.5)
probability_successes
```

There are three arguments: `success`, `trials` and `prob`. `success` means the number of successes, `trials` represents the number of trials, and `prob` is the probability of success on each trial.


## Show a data frame with the probability distribution

The function `bin_distribution()` is created to show a data frame with the probability distribution.

```{r}
dis1 <- bin_distribution(trials =5, prob = 0.5)
dis1
```

There are two arguments: `trials` and `prob`. `trials` represents the number of trials, and `prob` is the probability of success on each trial.


### Plot of the binomial probability distribution

You can use the function `plot()` to create a barplot to display the probability histogram of a binomial distribution.

```{r, fig.show='hold'}
plot(dis1)
```


## Show a data frame with the binomial cumulative distribution

The function `bin_cumulative()` is created to show a data frame with the binomial cumulative distribution.

```{r}
dis2 <- bin_cumulative(trials =5, prob = 0.5)
dis2
```

There are two arguments: `trials` and `prob`. `trials` represents the number of trials, and `prob` is the probability of success on each trial.


### Plot of the binomial cumulative distribution

You can use the function `plot()` to graph the binomial cumulative distribution.

```{r, fig.show='hold'}
plot(dis2)
```


## Show a list of trials and probability

The function `bin_variable()` is created to show a list with named elements `trials` and `prob`.

```{r}
bin1 <- bin_variable(trials =5, prob = 0.5)
bin1
```

There are two arguments: `trials` and `prob`. `trials` represents the number of trials, and `prob` is the probability of success on each trial.

The `summary()` function not only gives you a nice list of parameters trials and prob, but it also shows the mean, variance, mode, skewness and kurtosis.

```{r}
summary(bin1)
```


## Calculate the mean of a binomial distribution

The function `bin_mean()` is created to calculate the mean of a binomial distribution.

```{r}
me <- bin_mean(trials =5, prob = 0.5)
me
```

There are two arguments: `trials` and `prob`. `trials` represents the number of trials, and `prob` is the probability of success on each trial.


## Calculate the variance of a binomial distribution: bin_variance()

The function bin_variance() is created to calculate the variance of a binomial distribution.

```{r}
v <- bin_variance(trials =5, prob = 0.5)
v
```

There are two arguments: `trials` and `prob`. `trials` represents the number of trials, and `prob` is the probability of success on each trial.


## Calculate the mode of a binomial distribution: bin_mode()

The function bin_mode() is created to calculate the mode of a binomial distribution.

```{r}
mo <- bin_mode(trials =5, prob = 0.5)
mo
```

There are two arguments: `trials` and `prob`. `trials` represents the number of trials, and `prob` is the probability of success on each trial.


## Calculate the skewness of a binomial distribution: bin_skewness()

The function bin_skewness() is created to calculate the skewness of a binomial distribution.

```{r}
s <- bin_skewness(trials =5, prob = 0.5)
s
```

There are two arguments: `trials` and `prob`. `trials` represents the number of trials, and `prob` is the probability of success on each trial.


## Calculate the kurtosis of a binomial distribution: bin_kurtosis()

The function bin_kurtosis() is created to calculate the kurtosis of a binomial distribution.

```{r}
k <- bin_kurtosis(trials =5, prob = 0.5)
k
```

There are two arguments: `trials` and `prob`. `trials` represents the number of trials, and `prob` is the probability of success on each trial.
